Optimizing Large Scale Surveys for Photometric Calibration, \\ The Euclid Dark Energy Mission as an Example

### 2011-07-24 Documentation/cross_cal_paper.tex
euclid: clean directory
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@19088 03a3cea6-2c03-0410-ac9b-9271b1c66c29
euclid: correct typo in paper
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@19132 03a3cea6-2c03-0410-ac9b-9271b1c66c29

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\textwidth]{temp.png}
\end{center}
\caption{An example catalog of fake sources used within the simulations. The sources are shown at their position on a portion of the sky (left) and as a histogram of their magnitudes (right).
\label{fig:sky}}
\end{figure}

@@

We do not take into account this final term in our analysis and we therefoer assume that the uncertainty variance on the counts are:
\begin{displaymath}
\sigma_{{i}}^{2} = \alpha^{2} + \eta^{2}\, c^{2}_i
\end{displaymath}
\noindent{}where $\alpha$ and $\eta$ are both constants. In fact, we complicate the model by applying an extra term to the count's uncertainty variance, which we do not take into account in our analysis:

>>>>

%\begin{figure}[ht]
%\begin{center}
%\includegraphics[width=\textwidth]{temp.png}
%\end{center}
%\caption{An example catalog of fake sources used within the simulations. The sources are shown at their position on a portion of the sky (left) and as a histogram of their magnitudes (right).
%\label{fig:sky}}
%\end{figure}

@@

We do not take into account this final term in our analysis and we therefore assume that the uncertainty variance on the counts are:
\begin{displaymath}
\sigma_{{i}}^{2} = \alpha^{2} + \eta^{2}\, c^{2}_i
\end{displaymath}
\noindent{}where $\alpha$ and $\eta$ are both constants. In fact, we complicate the model by applying an extra term to the count's uncertainty variance, which we do not take into account in our analysis:
